\documentclass[../main.tex]{subfiles}
\begin{document}

\chapter{Week 2 — Research Design}
\label{ch:week2}

\textit{Snapshot and part summaries: see the overview on page~\pageref{ov:week2}.}

\section{Part 1 — Strategic Areas: Conceptual and Technical Design}
\label{sec:conceptual-technical}

\subsection{Content}
\begin{itemize}
  \item Research design has two strategic areas, \keyterm{conceptual research design} and \keyterm{technical research design}.
  \item Conceptual design models the content of the research and determines what, why, and how much is going to be studied.
  \item Conceptual design has four phases: the objective, the research framework, the research question and conceptual model, and definition and operationalisation.
  \item Technical design is the set of activities needed to realise the objectives set in the conceptual phase, and it concerns how, where, and when.
  \item Technical design has three phases: research strategy and research material, both answering how, and research planning, answering where and when.
\end{itemize}

\subsection{Explanation}
The two strategic areas are a clean division between deciding and doing, and the course is deliberate about which comes first. Conceptual design is the content layer, where the project commits to what it will study, why that is worth studying, and how much of it is in scope. Technical design is the execution layer, where the project commits to the instruments, the location, and the schedule. The reason conceptual must precede technical is that every technical choice is an answer to a conceptual question, so a method chosen before the objective is fixed is a method chosen for no stated purpose.

The phase counts are worth memorising because they organise the rest of the week. The four conceptual phases move from the objective, through the framework and the research question, to the operationalisation that hands concrete variables to the technical side. The three technical phases then take those variables and decide how to obtain them, with what materials, and on what timeline. The planning phase reaches forward into Week~5, where the same systems-engineering tools become full project management (\autoref{sec:project-mgmt}), so this part is the seam between research design and project execution.

\section{Part 2 — Conceptual Design: Objectives, Questions, and Operationalisation}
\label{sec:objectives-rqs}
\label{sec:operationalization}

\subsection{Content}
\begin{itemize}
  \item \keyterm{Theory-oriented objectives} are theory development, building a theory about something not yet known, and theory validation, testing whether a proposed variable relationship exists.
  \item \keyterm{Practice-oriented objectives} are problem analysis, diagnosis, design, and change.
  \item Problem analysis recommends what technological developments solve a problem, and diagnosis recommends how to improve or optimise a current situation.
  \item Design produces a solution to a technical problem, and change alters a practical situation and analyses the impact.
  \item The \keyterm{research objective} follows the template: the objective is (a) the contribution to the solution, by (b) the way that contribution is provided.
  \item \keyterm{Criteria for a good research objective}: informative, useful, feasible, and clear.
  \item \keyterm{Research questions} yield information useful and necessary for the objective and enable the technical design to be built.
  \item Formulate a question by naming the key concept, thinking qualitatively first, then linking to quantitative evidence and a testable main hypothesis.
  \item Pitfalls: the questions are yours to answer not the client's, there is never only one sub-question, and questions are open-ended rather than yes or no.
  \item Each question should be relevant, researchable, anchored, and precise, and a struggling technical design usually signals an inadequate question set.
  \item \keyterm{Research framework}: a schematic of the steps needed to answer the questions, naming the knowledge required and the methods, whether borrowed or developed.
  \item \keyterm{Operationalisation}: define key concepts exactly, state assumptions and what is neglected and why, then name the indicators or variables and how they are measured.
\end{itemize}

\subsection{Explanation}
The objective types are not interchangeable, and choosing among them is the first real commitment of the project. Theory-oriented work either builds a new theory or tests an existing relationship, while practice-oriented work runs along a spectrum from analysing a problem, through diagnosing and designing, to actively changing a situation and measuring the result. The objective template forces both halves of any objective into the open, since clause (a) states the contribution and clause (b) states the mechanism by which it is delivered. The four criteria then act as an acceptance test on that statement, asking whether a generic engineer would understand it, whether it benefits the problem, whether it fits the available resources, and whether it is precise about the contribution.

Research questions are the operational form of the objective, and the rules around them are practical guards rather than style points. The insistence on at least two sub-questions and on open-ended phrasing both push against the failure mode of a project that can be closed with a single yes or no, which would leave nothing to research. The relevant, researchable, anchored, and precise test mirrors the objective criteria at the level of each question. The framework then sequences the questions into a route, and the explicit invitation to reuse an existing method reflects the course view that a contribution can lie in the application or the combination of methods rather than in a new method itself. Operationalisation is the last conceptual act and the most consequential, because exact definitions, stated assumptions, named variables, and a measurement plan are precisely the inputs the technical design needs, and any vagueness left here surfaces later as a technical design that cannot be specified (\autoref{sec:strategy-materials}).

\section{Part 3 — Technical Design: Strategy, Materials, and Planning}
\label{sec:strategy-materials}

\subsection{Content}
\begin{itemize}
  \item \keyterm{Research strategy} takes the framework into practical terms and defines exactly how the research will be done.
  \item The strategy is judged on suitability of skills and problem level, availability of resources, achievable duration, and ethics.
  \item \keyterm{Research materials} are every tool needed, from a computer with specific software to complex laboratory equipment.
  \item Secure access to materials as early as possible, allow time to learn the tools, and expect failure points with contingencies ready.
  \item \keyterm{Research planning} sets the time frame for all activities, and because plans change it must allow flexibility.
  \item An initial plan includes milestones, deliverables, and holidays, and uses tools such as the Work Breakdown Structure, work flow diagram, and Gantt chart.
\end{itemize}

\subsection{Explanation}
The research strategy is where the theoretical framework first meets the constraints of the real world, and its four tests are a compressed feasibility study. Suitability asks whether the researcher and the problem are matched in skill and level, availability asks whether the needed resources can actually be obtained, duration asks whether the work fits the time, and ethics asks not only whether it can be done but whether it should. These are the same concerns Week~1 raised at the idea stage, now applied to a concrete plan rather than a topic. Materials are treated with unusual realism, since the guidance to secure access early, to budget learning time, and to plan for tools that fail is aimed squarely at the way technical projects actually slip.

Planning closes the technical design by attaching the work to a calendar, and its central message is that a plan is valuable precisely because it will change. Building in flexibility, naming milestones and deliverables, and even marking holidays are all ways of making the inevitable changes manageable rather than disruptive. The systems-engineering tools introduced here are named but not yet developed, because Week~5 returns to the Work Breakdown Structure and the Gantt chart and shows how they expose the critical path of a project (\autoref{sec:project-mgmt}). At this stage the point is simply that a schedule can only be assembled once the conceptual and technical designs are both in place, which is why planning sits last in the sequence.

\section{Part 4 — Ethics and Research Conduct}
\label{sec:ethics}

\subsection{Content}
\begin{itemize}
  \item Ensure the work is reproducible and can be traced back to original data, and keep the raw data.
  \item Verify the origin of any data that is given, and always give credit where it is due.
  \item Follow the university code of conduct as the governing standard for integrity.
  \item TU Delft operates the \keyterm{Human Research Ethics Committee (HREC)} as its ethics board for research involving people.
  \item Permission must be sought for any research involving human test subjects, including questionnaire and interview participants and testers such as test pilots.
\end{itemize}

\subsection{Explanation}
The general recommendations look like good habits but are better read as the operational meaning of integrity in a technical project. Reproducibility and traceability to original data are what allow a result to be checked, reused, and trusted, and keeping the raw data is the precondition for both. Verifying the origin of supplied data and giving credit are the two failure points most likely to surface as misconduct, since unverified inputs can invalidate a whole analysis and missing credit is the core of plagiarism. These duties are not separate from the technical work, because they dictate how data is recorded and stored, which is exactly what Week~4 reproducibility and Week~5 data management formalise.

The Human Research Ethics Committee marks the one place in the course where ethical review is a hard procedural gate rather than a matter of personal care. Any study that touches human participants, whether through a questionnaire, an interview, or a physical test with a person, needs permission before it can proceed. This matters for planning, because approval takes time and must be sequenced into the schedule rather than assumed. It also connects forward to the personal-data rules of Week~3, where the same human participants generate data that falls under data-protection law (\autoref{sec:data-sources}), so the ethical gate and the legal gate are two views of the same obligation.

\section{Reading Material}
\label{sec:reading2}

\begin{partbox}
The Week~2 reading is the TU Delft Code of Conduct, which sits behind the brief conduct slides and gives the values those rules express. Where the slides give instructions, the code gives the reasoning, framing integrity as a shared institutional commitment rather than a list of prohibitions.
\end{partbox}

\begin{itemize}
  \item The code is built on six core values: diversity, integrity, respect, engagement, courage, and trust.
  \item These values underpin the Integrity Statement, a set of basic principles every member of the community is expected to endorse and act upon.
  \item Integrity is framed as a collective responsibility, supported by an institutional integrity infrastructure of means, resources, and guidance.
  \item Its sections move from purpose and the core values, through acting with integrity and supporting integrity, to taking integrity further.
\end{itemize}

\end{document}
